---
title: "Data Science Document"
author: "Bryan Sandor"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# Answers to questions

- I think being a data scientist is about communicating analyses of data to a variety of disciplines with no assumptions regarding statistical background.

- My initial understanding of a statistician is more in line with what I think of as a data scientist, so I think more generally a statistician develops algorithms and methods that are then used by data scientists, eg. LASSO, Bayesian inference, etc. In this respect, I think every data scientist is a(n applied) statistician, but not vice-versa.

- Given what I've read in this week's materials, I think I am more akin to a data scientist than a statistician, despite my strong mathematics background. I am more interested in the interpretation of results than finding or strengthening new or existing methods.

# Code Sample

First we run the instructed code:

```{r}
y <- density(iris$Petal.Width)
```

Then we run code to examine the format of `y`

```{r}
class(y)
typeof(y)
structure(y)
```

Finally, we plot the graph of `y`

```{r}
#| echo: false
plot(y)
```
